---
output: html_document
---
CS 329E Data Visualization - DV_TableauProject2
===
**For this project, we use in-depth government census data that focuses on student obesity/overweight rates from elementary to high schools within New York. We utilize SQL commands such as Partition By and rank() in order to display crosstabs in R which match crosstabs made from the same data in Tableau**

**Authors: Bruno De Hoyos (bd8739), Estevan Garza (eg22453)**

###Importing data frames:

We begin by importing some useful libraries:

```{r, warning=FALSE}
require(bitops)
require(stats)
require(ggplot2)
require(grid)
require(plyr)
require(reshape2)
require(RCurl)
require(gplots)
require(tidyr)
require(dplyr)
require(jsonlite)
```



Our first crosstab ranks the regions across New York which have the highest obesity rates. WE also group these regions by each grade level using the PARTITION function in SQL.
```{r}
summary(cars)
```

The next crosstab involves displaying the difference in obesity numbers each region has, partitioned by grade level,from the whichever region has the respectively highest (max amount) rate of student obesity.
```{r, echo=FALSE}
plot(cars)
```

Our next crosstab displays the nth highest rate of obesity in a region given a grade level. In Tableau the nth slider bar allows the user to choose which tier of statistic he or she wants to see.

```{r}
summary(cars)
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



The last crosstab we reproduce involves displaying the cumulative distribution of obesity statistics across regions partitioned by grade level.  
```{r}
summary(cars)
```
